DOpElib:\\ Differential Equations and Optimization Environment

### 2018-10-15 Examples/Documentation/examples.tex

>>>>

  When working with cmake, the easiest option is to set 
  the DOpElib environment variable, so that it will be found 
  be cmake (similar to Section \ref{sec_installation}):
  \begin{verbatim}
  export DOPE_DIR=path_to_DOpElib
  \end{verbatim}
  or alternatively, passing directly a flag to cmake:
  \begin{verbatim}
  -DDOPE_DIR=path_to_DOpElib
  \end{verbatim}

### 2018-10-15 Examples/description.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib:\\ 
Differential Equations and Optimization Environment}
\author{
  Thomas Wick\thanks{Leibniz Universit\"at Hannover, 
    {thomas.wick@ifam.uni-hannover.de}}, 
  Winnifried Wollner\thanks{Technische Universität Darmstadt, 
    {wollner@mathematik.tu-darmstadt.de}}
}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib:\\ 
Differential Equations and Optimization Environment}
\author{
  Thomas Wick\thanks{Leibniz Universit\"at Hannover, 
    {thomas.wick@ifam.uni-hannover.de}} 
   $\,$ and $\,$
  Winnifried Wollner\thanks{Technische Universität Darmstadt, 
    {wollner@mathematik.tu-darmstadt.de}}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Documentation/terminal_output.tex}
